A Language's Unigram Entropy Distribution Predicts Self-Paced Reading Times

### 2019-01-11 cogsci/position-info.Rmd
worked on cogsci

The *wrap-up effect* is a popular hypothesis within the eye-tracking community. The hypothesis states that, in written text, sentence-final words are processed more slowly on average then sentence-medial or sentence-initial words, due to readers integrating information from the entire sentence in order to form a final, coherent thought expressed by the sentence, among other reasons. With these two ideas, information production distribution in spoken and written communication, and information integration in reading written texts, we move on to discuss cross-linguistic differences in the distribution of information across sentences.

@@

The unigram entropy measure does not directly take into account the context of the utterance.

Figure for the method.

@@

We also ran this analysis on Spanish, German, Mandarin and Japanese corpora from CHILDES. The Spanish corpus we used was the XXX and the German corpus we used was the XXX. The Mandarin corpus we used was the XXX and the Japanese corpus we used was the XXX. For Mandarin, we used pinyin transliterations of the utterances in the corpus with demarcated word boundaries, and for Japanese we used romanji transliterations of words in the corpus. Japanese Hiragana, Katakana and Kanji writing systems, and the Chinese characters used for writing Mandarin do not normally demarcate word boundaries. JUSTIFICATION FOR WHY THE TRANSLITERATIONS ARE OKAY.

@@

# Wikipedia Data
We also wanted to apply this analysis to large-scale text data, to compare with the parent-child speech data results from using CHILDES. Using Giuseppe Attardi's Wikiextractor tool \footnote{https://github.com/attardi/wikiextractor}, we extracted the text corpora for $165$ languages from Wikipedia. Each language corpus was cleaned and limited to sentences between $6$ and $50$ words. Similar to the data from CHILDES, we divided each corpus by sentence length, and then computed the unigram entropy measure on each word position within each sentence length. HOW DID WE JOIN TOGETHER SENTENCE LENGTHS

>>>>

@@

The unigram entropy measure works as

Figure for the method?

@@

We also ran this analysis on Spanish, German, Mandarin and Japanese corpora from CHILDES. The Spanish corpus we used was the XXX and the German corpus we used was the XXX. The Mandarin corpus we used was the XXX and the Japanese corpus we used was the XXX. For Mandarin, we used pinyin transliterations of the utterances in the corpus with demarcated word boundaries, and for Japanese we used romanji transliterations of words in the corpus. Japanese Hiragana, Katakana and Kanji writing systems, and the Chinese characters used for writing Mandarin do not normally demarcate word boundaries by spacing words apart, and for normal Japanese and Chinese writing including spaces between word boundaries can have a negative effect on reading times (Sainio et al, 2007; Bai et al, 2008).

@@

# Wikipedia Data
We also wanted to apply this analysis to large-scale text data, to compare with the parent-child speech data results from using CHILDES. Using Giuseppe Attardi's Wikiextractor tool \footnote{https://github.com/attardi/wikiextractor}, we extracted the text corpora for $165$ languages from Wikipedia by downloading the data dump of Wikipedia. Each language corpus was cleaned and limited to sentences between $6$ and $50$ words. Similar to the data from CHILDES, we divided each corpus by sentence length, and then computed the unigram entropy measure on each word position within each sentence length. HOW DID WE JOIN TOGETHER SENTENCE LENGTHS

## Clustering

# Conclustions and future research
The *wrap-up effect* is a popular hypothesis within the eye-tracking community. The hypothesis states that, in written text, sentence-final words are processed more slowly on average then sentence-medial or sentence-initial words, due to readers integrating information from the entire sentence in order to form a final, coherent thought expressed by the sentence, among other reasons. With these two ideas, information production distribution in spoken and written communication, and information integration in reading written texts, we move on to discuss cross-linguistic differences in the distribution of information across sentences.

### 2019-01-11 cogsci/position-info.tex
worked on cogsci

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

@@

{\centering \includegraphics{figs/yunigram-1}

\caption[English entropy distribution for three sentence lengths from BNC]{English entropy distribution for three sentence lengths from BNC}\label{fig:yunigram}
\end{figure*}
\end{CodeChunk}

\section{Our Methods}\label{our-methods}

We used the CHILDES TalkBank (Brown 1973; MacWhinney 2000) corpora
database of spoken adult-child conversations. We first used the Brown
and Providence English corpora from CHILDES. The Brown corpus contains
conversations between three young children (over 1.5 years old and under
6 years old) and their families in the home. The Providence corpus
contains transcriptions of audio/video files which recorded interactions
between children between 1 and 3 years old and their parents in the
home.

@@

We found a similar distribution for Spanish and German corpora from
CHILDES. The Spanish corpus we used was the XXX and the German corpus we
used was the XXX.

\section{Formalities, Footnotes, and
Floats}\label{formalities-footnotes-and-floats}

Use standard APA citation format. Citations within the text should
include the author's last name and year. If the authors' names are
included in the sentence, place only the year in parentheses, as in
(1972), but otherwise place the entire reference in parentheses with the
authors and year separated by a comma (Newell \& Simon, 1972). List
multiple references alphabetically and separate them by semicolons
(Chalnick \& Billman, 1988; Newell \& Simon, 1972). Use the et. al.
construction only after listing all the authors to a publication in an
earlier reference and for citations with four or more authors.

For more information on citations in RMarkdown, see
\textbf{\href{http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html\#citations}{here}.}

\subsection{Footnotes}\label{footnotes}

Indicate footnotes with a number\footnote{Sample of the first
footnote.} in the text. Place the footnotes in 9 point type at the
bottom of the page on which they appear. Precede the footnote with a
horizontal rule.\footnote{Sample of the second footnote.} You can also
use markdown formatting to include footnotes using this
syntax.\footnote{Sample of a markdown footnote.}

\subsection{Figures}\label{figures}

All artwork must be very dark for purposes of reproduction and should
not be hand drawn. Number figures sequentially, placing the figure
number and caption, in 10 point, after the figure with one line space
above the caption and one line space below it. If necessary, leave extra
white space at the bottom of the page to avoid splitting the figure and
figure caption. You may float figures to the top or bottom of a column,
or set wide figures across both columns.

\subsection{Two-column images}\label{two-column-images}

You can read local images using png package for example and plot it like
a regular plot using grid.raster from the grid package. With this method
you have full control of the size of your image. \textbf{Note: Image
must be in .png file format for the readPNG function to work.}

You might want to display a wide figure across both columns. To do this,
you change the \texttt{fig.env} chunk option to \texttt{figure*}. To
align the image in the center of the page, set \texttt{fig.align} option
to \texttt{center}. To format the width of your caption text, you set
the \texttt{num.cols.cap} option to \texttt{2}.

{\centering \includegraphics{figs/2-col-image-1}

\caption[This image spans both columns]{This image spans both columns. And the caption text is limited to 0.8 of the width of the document.}\label{fig:2-col-image}
\end{figure*}
\end{CodeChunk}

\subsection{One-column images}\label{one-column-images}

Single column is the default option, but if you want set it explicitly,
set \texttt{fig.env} to \texttt{figure}. Notice that the
\texttt{num.cols} option for the caption width is set to \texttt{1}.

\begin{CodeChunk}
\begin{figure}[H]

{\centering \includegraphics{figs/image-1}

\caption[One column image]{One column image.}\label{fig:image}
\end{figure}
\end{CodeChunk}

\subsection{R Plots}\label{r-plots}

You can use R chunks directly to plot graphs. And you can use latex
floats in the fig.pos chunk option to have more control over the
location of your plot on the page. For more information on latex
placement specifiers see
\textbf{\href{https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions}{here}}

\begin{CodeChunk}
\begin{figure}[H]

{\centering \includegraphics{figs/plot-1}

\caption[R plot]{R plot}\label{fig:plot}
\end{figure}
\end{CodeChunk}

\subsection{Tables}\label{tables}

Number tables consecutively; place the table number and title (in 10
point) above the table with one line space above the caption and one
line space below it, as in Table 1. You may float tables to the top or
bottom of a column, set wide tables across both columns.

You can use the xtable function in the xtable package.

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & -0.10 & 0.11 & -0.9 & 0.37 \\ 
  x & 1.97 & 0.12 & 16.6 & 0.00 \\ 
   \hline
\end{tabular}
\caption{This table prints across one column.} 
\end{table}

@@

\hypertarget{refs}{}
\hypertarget{ref-ChalnickBillman1988a}{}
Chalnick, A., \& Billman, D. (1988). Unsupervised learning of
correlational structure. In \emph{Proceedings of the tenth annual
conference of the cognitive science society} (pp. 510--516). Hillsdale,
NJ: Lawrence Erlbaum Associates.

\hypertarget{ref-NewellSimon1972a}{}
Newell, A., \& Simon, H. A. (1972). \emph{Human problem solving}.
Englewood Cliffs, NJ: Prentice-Hall.

>>>>

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{apacite}

% KM added 1/4/18 to allow control of blind submission

@@

\section{Methods}\label{methods}

We used the CHILDES TalkBank (Brown 1973; MacWhinney 2000) corpora
database of spoken adult-child conversations. We first used the Brown
and Providence English corpora from CHILDES. The Brown corpus contains
conversations between three young children (over 1.5 years old and under
6 years old) and their families in the home. The Providence corpus
contains transcriptions of audio/video files which recorded interactions
between children between 1 and 3 years old and their parents in the
home. We divided each corpus by speaker into child and non-child
categories. We further divided the corpora by utterance length, so that
all sentences of length \(k\) (e.g. \(6\)) were grouped together.
Finally, within each utterance length, we computed the unigram entropy
measure for each position.

The unigram entropy measure works as

Figure for the method?

Plots for the entropy distributions are below. The adult and child
unigram entropy distributions track one another extremely well, with the
child distribution for each sentence length having relatively lower
entropy.

@@

We also ran this analysis on Spanish, German, Mandarin and Japanese
corpora from CHILDES. The Spanish corpus we used was the XXX and the
German corpus we used was the XXX. The Mandarin corpus we used was the
XXX and the Japanese corpus we used was the XXX. For Mandarin, we used
pinyin transliterations of the utterances in the corpus with demarcated
word boundaries, and for Japanese we used romanji transliterations of
words in the corpus. Japanese Hiragana, Katakana and Kanji writing
systems, and the Chinese characters used for writing Mandarin do not
normally demarcate word boundaries by spacing words apart, and for
normal Japanese and Chinese writing including spaces between word
boundaries can have a negative effect on reading times (Sainio et al,
2007; Bai et al, 2008).

\section{Results}\label{results}

We found a distinct three-step distribution for English, Spanish and
German CHILDES corpora, with a slight dip in the penultimate position of
each sentence. The Mandarin and Japanese data, by comparison,

\section{Analysis}\label{analysis}

\section{Wikipedia Data}\label{wikipedia-data}

We also wanted to apply this analysis to large-scale text data, to
compare with the parent-child speech data results from using CHILDES.
Using Giuseppe Attardi's Wikiextractor tool
\footnote{https://github.com/attardi/wikiextractor}, we extracted the
text corpora for \(165\) languages from Wikipedia by downloading the
data dump of Wikipedia. Each language corpus was cleaned and limited to
sentences between \(6\) and \(50\) words. Similar to the data from
CHILDES, we divided each corpus by sentence length, and then computed
the unigram entropy measure on each word position within each sentence
length. HOW DID WE JOIN TOGETHER SENTENCE LENGTHS

\subsection{Clustering}\label{clustering}

\section{Conclustions and future
research}\label{conclustions-and-future-research}

@@

\bibliographystyle{apacite}
